\documentclass[12pt]{article}

\renewcommand{\familydefault}{\sfdefault}

% IDEA: partition entries into separate pages to force team communication
%
% Question ideas:
%
% Halftime: Read Snake monologue
% IDEA: put real S3 definition on back of halftime monologue sheet
% IDEA: put real S3 definition on separate sheet, hide in bathroom, set up
% Github Page explaining where to find it, put tinyurl link on inside of
% envelope containing halftime monologues
% IDEA: have teams pick names out of hat, (decoy, liquid, raging, ... and
% snake, ocelot, mama, ... etc.)
%
% Final ideas:
% Reconstruct timeline
% Character web
%
% Virtuous Mission
% Operation Snake Eater
% Les Enfants Terribles
% Big Boss is killed by Solid Snake in Zanzibarland
% Shadow Moses Incident
% Big Shell Incident
% The War Economy is instituted
%
% 1. Match pictures of Snakes with their codenames
%
% What does the S3 plan stand for?
%
% Why is Vamp seemingly immortal (nanomachines, one word answer, deduce from
% cheat sheet)
%
% Which character slept with his stepmom?
%
% Two different impersonations occur during the Shadow Moses Incident. For
% both, name the impersonator and who they impersonated.
%
% What do Deepthroat and Mr. X have in common?
% 
% Match characters to their supernatural abilities
%
%
%
%
%
%
% Match characters to event they were a part of (maybe split into two questions
% for heros and villains)
%
% What two units have matching codenames (FOXHOUND and BB)
% Which character's real name is...
%
% Match first parts of character names with last part (not that good, can look
% at just character names)


\title{Metal Gear Solid Cheat Sheet}
\date{}

\begin{document}
\maketitle
\begin{description}
	\item [Arsenal Gear] is a submersible mobile fortress that can control
		internet communications. It is also equipped with nuclear
		weapons. It houses GW.

	\item [The Beauty and the Beast Unit] is a group of female soldiers
		outfitted with advanced suits. Each suffers from intense PTSD,
		and believe that killing Solid Snake will ease their anguish.
		They are each hired by various PMCs as field commanders. The
		unit consists of Laughing Octopus, Raging Raven, Crying Wolf,
		and Screaming Mantis.

	\item [Big Boss] \textit{(Real name John, AKA Jack, Snake, Naked Snake,
		Boss)} is the main playable character in Metal Gear Solid 3.
		Considered to be the greatest soldier to ever live, he
		eventually betrays the United States in an effort to create
		Outer Heaven. He was cloned several times as a part of the Les
		Enfants Terribles project, and is ultimately killed by one of
		these clones (Solid Snake) in Zanzibarland. During Operation
		Snake Eater, he wears a bandana belonging to The Boss. He also
		wears an eye patch on his right eye due to it being shot out
		during the operation.
	
	\item [The Big Shell] is (seemingly) an offshore cleanup facility
		constructed after the sinking of an oil tanker off the coast of
		Manhattan. In reality, the Big Shell is a front for Arsenal
		Gear.

	\item [The Big Shell Incident] was an incident where Dead Cell took
		hostage of President Johnson and several others aboard the Big
		Shell. They supposedly demanded \$30 billion, and threatened to
		destroy the Big Shell otherwise, which would theoretically lead
		to an ecological disaster. It is slowly revealed that the
		entire event, including the sinking of the tanker that
		necessitated the Big Shell's construction, Dead Cell's takeover
		of the facility, and the individual deaths that occurred during
		the incident, were orchestrated by the Patriots as a part of
		the S3 Plan.

	\item [The Boss] \textit{(AKA The Joy)} is the ``Mother of Special
		Forces,'' the leader of the Cobra Unit, and the mentor of Big
		Boss. She defects to the Soviet Union, and Big Boss is sent to
		kill her as a part of Operation Snake Eater. Her philosophy has
		a major influence on Big Boss's thoughts and actions throughout
		his life.

	\item [The Cobra Unit] was a World War II special forces unit
		consisting of soldiers named after the emotions they
		experienced on the battlefield. The members were The Pain, The
		Fear, The End, The Fury, The Sorrow, and The Joy.

	\item [Colonel Campbell] is Solid Snake's commanding officer during the
		Shadow Moses Incident. For much of the Big Shell Incident, he
		is also seemingly the CO of Raiden, but it is eventually
		revealed that Raiden has actually been communicating with a
		Patriot AI impersonating the Colonel.

	\item [Cyborg Ninja] may refer to any of three characters that become
		cyborg ninjas throughout the series: Gray Fox, Olga
		Gurlukovich, or Raiden.

	\item [Dead Cell] is a terrorist organization consisting of Solidus
		Snake, Vamp, Fortune, and Fatman. Originally a government
		anti-terrorist training group, they were framed for civilian
		deaths by the Patriots, which drove them to commit real acts of
		terrorism. During the Big Shell Incident, they supposedly
		demand \$30 billion, but their real goal is to take control of
		Arsenal Gear and overthrow the Patriots.
		
	\item [Decoy Octopus] is a member of FOXHOUND and a master of disguise.
		It is eventually revealed that he died near the beginning of
		the Shadow Moses Incident while he was disguised as Donald
		Anderson due to exposure to FOXDIE.

	\item [Donald Anderson] \textit{(AKA Sigint)} is a radio contact of Big
		Boss during the Virtuous Mission and Operation Snake Eater. He
		later becomes the chief of DARPA and is involved in the
		production of Metal Gear REX. Solid Snake seems to meet him
		near the beginning of the Shadow Moses Incident, and he
		explains REX's deactivation procedure. However, it is later
		revealed that he actually died while being tortured by Ocelot
		before Snake's deployment (this was intentional on Ocelot's
		part, as Anderson knew Ocelot's true allegiance). The man Snake
		actually met was Decoy Octopus, who actually gave him REX's
		activation procedure, leading Snake to unwittingly activate
		REX.

	\item [Drebin] is an arms dealer who is able to bypass the Sons of the
		Patriots system. Solid Snake is able to send weapons to Drebin,
		who overrides their ID locks for a fee. Fun fact: he's named
		after Frank Drebin from The Naked Gun, because he gives
		Snake\ldots naked guns. Get it?

	\item [Emma Emmerich] \textit{(AKA E.E.)} is Otacon's step-sister. She
		is the creator of GW. She also develops a worm cluster to
		destroy GW during the Big Shell Incident. She is afraid of
		water because when she was a child, Otacon slept with her mom,
		and her step-dad was so overwhelmed at being cucked by his own
		son that he drowned himself and nearly drowned her. This is
		brought up out of nowhere while she is dying in Otacon's arms
		and then never mentioned again.

	\item [The End] is a member of the Cobra Unit. He is a 100-year-old
		sniper with the ability to lie dormant for weeks waiting for a
		shot on his target. This is because he was infected with a
		parasite that allows him to photosynthesize. The player can
		eliminate him either by fighting him in a prolonged
		stealth-based boss fight, by sniping him at a specific time
		before the fight, or by saving the game, waiting a week in real
		time, then starting the game again (by which point he will have
		died of old age).

	\item [EVA] \textit{(AKA Tatyana, Matka Pluku, Big Mama)} is one of Big
		Boss's contacts during Operation Snake Eater. She eventually
		becomes the surrogate mother to the clones of Big Boss.

	\item [Fatman] is a member of Dead Cell. He is an overweight explosives
		expert who travels on roller skates. Yes, I'm serious.
	
	\item [Fortune] is a member of Dead Cell. She has a supernatural ability
		to not die; bullets curve around her, and grenades thrown at
		her fail to explode. Unfortunately (ha) for her, her greatest
		desire is to die. In lieu of that, she walks around shooting
		people with a railgun. It is eventually revealed that her luck
		is brought on by a device unknowingly planted on her by the
		Patriots. Ocelot deactivates this and kills her.

	\item [FOXDIE] is an engineered virus, programmed to target specific
		people. Victims appear to die via heart attack. It was deployed
		during the Shadow Moses Incident to kill the members of
		FOXHOUND and the president of the company developing Metal Gear
		REX. However, Naomi Hunter also programmed the virus to target
		Solid Snake.

	\item [FOXHOUND] is a United States military unit founded by Big Boss,
		and led at various points by Big Boss, Colonel Campbell, and
		finally by Liquid Snake as a rogue unit. Solid Snake and Gray
		Fox are both members of this unit before the Shadow Moses
		Incident. The rogue unit is comprised of Liquid Snake, as well
		as Revolver Ocelot, Vulcan Raven, Sniper Wolf, Psycho Mantis,
		and Decoy Octopus.

	\item [Gekko] are Metal Gear-like fighting vehicles. Unlike other Metal
		Gears, their legs are made out of artificial muscle, making
		them more mobile. They are not capable of launching nuclear
		weapons. Also, their muscles build up lactic acid, which they
		eject by shitting. Also, they moo for some reason.

	\item [Gray Fox] \textit{(Real name Frank Jaeger, AKA Deepthroat)} is a
		former member of FOXHOUND. He is seemingly killed by Solid
		Snake before the Shadow Moses Incident, but returns as a cyborg
		ninja during the incident. He is killed by Liquid Snake, but
		not before imparting some final words of wisdom on Snake:
		``We're not tools of the government, or anyone else. Fighting
		was the only thing I was good at, but at least I fought for
		what I believed in.'' Snake later refers to him as a great
		friend, even though they tried to kill each other multiple
		times. C'est la vie.
		
	\item [GW] is one of the Patriots' AIs. It is responsible for the
		censoring of digital information, and the Big Shell Incident is
		orchestrated as a testing ground for its capabilities. It also
		controls the weaponry (including nuclear) of the United States
		military.

	\item [Johnny Sasaki] \textit{(AKA Akiba)} is a soldier working for
		FOXHOUND during the Shadow Moses Incident and for Dead Cell
		during the Big Shell Incident. His only defining character
		trait is his irritable bowel syndrome. In Metal Gear Solid 4,
		they decide to make him an important character for some reason,
		even though his defining character trait is still his IBS.

	\item [James Johnson] is the president of the United States during the
		Big Shell Incident. His election was orchestrated by the
		Patriots, as is the entire democratic process. He is killed by
		Ocelot after revealing the existence of the Patriots to Raiden.

	\item [Les Enfants Terribles] \textit{(French: ``The Terrible
		Children'')} was a United States government project that
		created clones of Big Boss. Two twins, Solid and Liquid Snake,
		were born, along with Solidus Snake. All three had their genes
		modified to make them sterile and experience accelerated aging
		as a fail-safe in case they betrayed the government (Solidus's
		is more rapid, making him appear older than the other two
		despite being the youngest). Furthermore, Solid and Liquid's
		genes were modified to make them ``inferior'' and ``superior''
		clones, respectively. Solidus, other than the stated
		modifications, is an exact clone of Big Boss.

	\item [Liquid Ocelot] \textit{(AKA Liquid)} is the name given to Liquid
		Snake when his spirit is possessing Revolver Ocelot's body.
		After this occurs, he seeks to overthrow the Patriots by
		seizing control of the Sons of the Patriots system. The
		possession occurs because Ocelot's hand was cut off by Gray
		Fox, and he replaces it with Liquid's corpse's hand. However,
		Ocelot is also the son of The Sorrow, a medium, which lets
		Liquid possess him. So it make sense when you think about it.

	\item [Liquid Snake] \textit{(AKA Liquid)} is a clone of Big Boss and
		the twin brother of Solid Snake. He has been led to believe
		that he was constructed to be the ``inferior'' clone of Big
		Boss, while Solid Snake was the superior (in reality, the
		opposite is true). He deeply resents this, and it drives him to
		surpass his supposed genetic destiny. He is ultimately killed
		by FOXDIE. However, his spirit later possesses Ocelot's body.
		Unlike his brothers, Liquid never wears an eye patch.

	\item [Little Gray] is Drebin's pet monkey. He has an addiction to soda
		and cigarettes.

	\item [Metal Gear] is a class of bipedal tanks, typically capable of
		launching nuclear weapons.

	\item [Metal Gear RAY] is a model of Metal Gear utilized by Dead Cell
		during the Big Shell Incident. It is not capable of launching
		nuclear weapons, and was designed more as an ``anti-Metal
		Gear'' after REX's data was leaked.

	\item [Metal Gear REX] is a Metal Gear model utilized by FOXHOUND
		during the Shadow Moses Incident. It is capable of launching
		nuclear weapons undetectable by early alert systems by using a
		railgun. It is ultimately destroyed by Solid Snake. After the
		incident, its technical details were leaked by Ocelot, which
		led to the proliferation of Metal Gears.

	\item [Master Miller] is (seemingly) one of Solid Snake's radio
		contacts during the Shadow Moses Incident. Snake knows him from
		previous missions. However, it is later revealed that Miller
		was killed before the incident, and the radio contact is
		actually Liquid Snake in disguise.

	\item [Nanomachines] are small machines that can modify humans in
		numerous ways, including enhancing combat abilities,
		restricting speech, and even rapidly healing otherwise fatal
		wounds.
	
	\item [Naomi Hunter] is one of Solid Snake's radio contacts during the
		Shadow Moses Incident. She is the adoptive sister of Gray Fox,
		and secretly resents Snake for seemingly killing him before the
		incident. Because of this, she reprograms FOXDIE to kill Snake
		at some random time in the future in addition to the other
		targets. She later regrets this and encourages Snake to
		``live'' while he can.

	\item [Next-Generation Special Forces] \textit{(AKA Genome Soldiers)}
		are a military unit that serve as the reserve members of
		FOXHOUND. They operate under Liquid Snake's command during the
		Shadow Moses Incident, thanks in part to brainwashing by Psycho
		Mantis. They have undergone gene therapy using Big Boss's DNA
		to make them more elite soldiers. Because of this, Liquid
		regards them as siblings. FOXHOUND demands the remains of Big
		Boss to help the soldiers, who are suffering from genetic
		disorders due to their treatments. Despite their advanced
		genetic makeup, they are frequently confused by footprints in
		the snow and moderately loud noises, and are unable to spot
		Solid Snake if he is not immediately in front of them.
	
	\item [Olga Gurlukovich] \textit{(AKA Mr.\ X)} is a Russian mercenary.
		Her Gurlukovich forces, led by her after her father's death,
		work with Dead Cell during the Big Shell Incident. She is later
		revealed to be the cyborg ninja who has been helping Raiden in
		his mission. This is because the Patriots are holding her child
		hostage, who will be killed if Raiden fails his mission.

	\item [Operation Snake Eater] was a mission undertaken by Big Boss
		after the failure of the Virtuous Mission. The objectives of
		the mission were to eliminate The Boss and Volgin, and destroy
		the Shagohod.

	\item [Otacon] \textit{(Real name Hal Emmerich)} is an engineer and the
		chief architect of Metal Gear REX. After the Shadow Moses
		Incident, he works with Solid Snake to rid the world of Metal
		Gears. He has a bad habit of falling in love with girls who pay
		even the slightest bit of attention to him and then blubbering
		like an idiot when they die. Also, look at his first name. Guess
		who he's named after! And he works with a guy whose real name
		is Dave?! Metal Gear is awesome.

	\item [Outer Heaven] is a concept originated by Big Boss that broadly
		refers to his dream of a world where soldiers won't be used as
		pawns of their governments.

	\item [The Patriots] \textit{(AKA The La-li-lu-le-lo)} are a secret
		organization that controls the entire United States, including
		its economy, politics, and military. By the time of the Shadow
		Moses Incident, the Patriots are purely a set of AIs. Certain
		people aware of the Patriot's existence are forced by their
		nanomachines to refer to them as the La-li-lu-le-lo to keep the
		organization's real name a secret.

	\item [The Philosophers] were a precursor to the Patriots. They were a
		secret organization of the most powerful figures in the United
		States, the Soviet Union, and China who formed a pact to create
		a new world order. The group eventually dissolved.

	\item [The Philosopher's Legacy] is a \$100 billion dollar fund amassed
		by the Philosophers to finance research and operations. When
		the group dissolved, the money was divided and hidden across
		the world.

	\item [Psycho Mantis] is a member of FOXHOUND with telekinetic,
		mind-reading, and brainwashing abilities. He is able to move
		the player's controller while flat on the ground and tell what
		games the player plays. He can be defeated by switching the
		controller from port 1 to port 2, rendering him unable to read
		Solid Snake's movements ahead of time.

	\item [Raiden] \textit{(Real name Jack, AKA Jack the Ripper, White
		Devil, Snake (briefly))} is the main playable character in
		Metal Gear Solid 2. He is deployed during the Big Shell
		Incident to resolve the terrorist threat. However, over the
		course of the incident, Raiden learns that very little about
		his mission is what it seems. Namely, the leader of the
		terrorist group is actually his adoptive father who made him
		fight in the Liberian Civil War as a child soldier, his
		commanding officer is an AI, his girlfriend was planted to spy
		on him, and the entire incident was planned by the Patriots to
		see how well they could control him. This all causes him to
		question his reality and ultimately become a cyborg ninja.

	\item [Revolver Ocelot] \textit{(Real name Adamska, AKA Ocelot,
		Shalashaska)} is a Russian gunslinger. He is a member of
		FOXHOUND during the Shadow Moses Incident, where his hand is
		sliced off by Gray Fox. It is revealed after the incident that
		he was actually a double agent, working for Solidus Snake.
		Several years later, he works with Solidus during the Big Shell
		Incident, and has replaced his hand with Liquid's corpse's
		hand. It is then revealed that he is again a double agent, and
		is truly working for the Patriots. However, he is then
		possessed by Liquid through his hand. During the Virtuous
		Mission and Operation Snake Eater, he works under Volgin.

	\item [Rosemary] is Raiden's girlfriend, and one of his radio contacts
		during the Big Shell Incident. It is eventually revealed that
		their chance encounter where they first met was orchestrated by
		the Patriots, and Rose was really just there to keep tabs on
		Raiden. However, she eventually caught real feelings for him.

	\item [The Shadow Moses Incident] was an incident where Next-Generation
		Special Forces and FOXHOUND, under the leadership of Liquid
		Snake, took over Shadow Moses Island. They demanded \$1
		billion and the remains of Big Boss, and threatened the launch
		of a nuclear weapon. Solid Snake was deployed to stop the
		threat. During the mission, he learned of the existence of
		Metal Gear REX. He also eventually learns that before the
		mission, he was infected with FOXDIE in an attempt by the
		United States government to retrieve REX undamaged. With the
		exception of Revolver Ocelot, every member of FOXHOUND was
		eliminated, either by Snake or by FOXDIE. REX was also
		destroyed. Consequently, the United States planned to bomb the
		island to cover up the events of the incident, but this is
		narrowly called off. Later, one of the members of Snake's radio
		team wrote a book exposing what occurred during the mission.

	\item [Shagohod] is an early competitor to Metal Gear. Unlike a Metal
		Gear, the Shagohod is not bipedal. It launches nuclear weapons
		by accelerating to high speeds, extending its range.
	
	\item [Sokolov] is a scientist and lead architect of the Shagohod.

	\item [Solid Snake] \textit{(Real name David, AKA Snake, Iroquois
		Pliskin)} is the main playable character of Metal Gear, Metal
		Gear 2, Metal Gear Solid, part of Metal Gear Solid 2, and Metal
		Gear Solid 4. He is one of the products of the Les Enfants
		Terribles project. Unlike his brothers, Snake accepts his
		origins as a clone. He seeks out a life of his own, refusing to
		be chained to fate. Several believe that he enjoys killing,
		although he denies this. He also denies being a hero, declaring
		that he simply fights for what he believes in. He typically
		wears a bandana when deployed. Later, Snake wears a hi-tech eye
		patch over his still-functioning left eye to give him advanced
		data during deployment.

	\item [Solid Snake Simulation] \textit{(AKA the S3 Plan)} is a secret
		plan carried out by the Patriots during the Big Shell Incident.
		It turns out that the entire incident was constructed by the
		Patriots to be similar to the Shadow Moses Incident in key
		ways. For instance, both incidents are spearheaded by a
		``Snake,'' both carry the threat of a nuclear strike, and both
		involve the appearance of a cyborg ninja, among numerous other
		similarities. Ocelot eventually reveals that this was all to
		test the feasibility of turning any soldier into a soldier on
		par with Solid Snake.

	\item [Solidus Snake] \textit{(Real name George Sears, AKA Solidus,
		Solid Snake (briefly))} is the president of the United States
		during the Shadow Moses incident. He is a product of the Les
		Enfants Terribles project. His resentment of the Patriots and
		his desire to be remembered by history drives him to lead Dead
		Cell to take over the Big Shell. He loses his left eye during
		the incident and wears an eye patch as a result. He also kills
		Raiden's biological parents and forces him to fight as a child
		soldier. He also has wears a suit with mechanical tentacles.
		You also have a sword fight with him at the end of MGS2. Metal
		Gear is awesome.

	\item [Sons of the Patriots] is a system of the Patriots that controls
		the world's soldiers in various ways through nanomachines. The
		system enhances and regulates their experiences on the
		battlefield, and also controls their access to weapons by
		ID-locking them. However, gun launderers like Drebin are able
		to bypass this component of the system.
	
	\item [Vamp] is a member of Dead Cell. He is a bisexual vampire who is
		seemingly immortal.

	\item [The Virtuous Mission] was a failed operation undertaken by Big
		Boss to extract Sokolov from the Soviet Union. The mission
		ended with the defection of The Boss and a nuclear warhead
		being fired at the Soviet Union by Volgin, necessitating
		Operation Snake Eater to ease the resulting tensions between
		the United States and the Soviet Union.

	\item [Volgin] is a GRU colonel who seeks to overthrow Khrushchev.
		After The Boss's defection, he fired a nuclear warhead at the
		Soviet Union, framing the United States for it. He possesses a
		microfilm containing records of where the Philosopher's Legacy
		is hidden. His body carries a permanent electric charge, and he
		can control this charge to electrocute people.
	
	\item [The War Economy] is a new economic structure instituted by the
		Patriots which turned war into a business. This led to the
		proliferation of private military companies fighting
		never-ending wars. The Sons of the Patriots system artificially
		controls the intensity of these wars.

	\item [Zero] \textit{(Real name David Oh, AKA Major Tom (briefly))} is
		Big Boss's commanding officer during the Virtuous Mission and
		Operation Snake Eater.
\end{description}

\newpage

\section*{Quotes}
\begin{quote}
	``Life isn't just about passing on your genes. We can leave behind much
	more than just DNA. Through speech, music, literature and movies\ldots
	what we've seen, heard, felt\ldots anger, joy and sorrow\ldots these
	are the things I will pass on. That's what I live for. We need to pass
	the torch, and let our children read our messy and sad history by its
	light. We have the magic of the digital age to do that with. The human
	race will probably come to an end some time, and new species may rule
	over this planet. Earth may not be forever, but we still have the
	responsibility to leave what trace of life we can. Building the future
	and keeping the past alive are one in the same thing.''

	``War\ldots has changed. It's no longer about nations, ideologies, or
	ethnicity. It's an endless series of proxy battles fought by
	mercenaries and machines. War, and its consumption of life, has become
	a well-oiled machine. War has changed. ID-tagged soldiers carry
	ID-tagged weapons, use ID-tagged gear. Nano-machines inside their
	bodies enhance and regulate their abilities. Genetic control,
	information control, emotion control\ldots battlefield control.
	Everything is monitored and kept under control. War --- has changed.
	The age of deterrence has become the age of control. All in the name of
	averting catastrophe from Weapons of Mass Destruction. And he who
	controls the battlefield, controls history. War has changed\ldots When
	the battlefield is under total control, war becomes routine.''
\end{quote}

\pagebreak

\begin{description}
	\item [Selection for Societal Sanity] \textit{(AKA the S3 Plan)} is a
		secret plan carried out by the Patriots during the Big Shell
		Incident. It turns out that the entire incident was constructed
		by the Patriots to be similar to the Shadow Moses Incident in
		key ways. For instance, both incidents are spearheaded by a
		``Snake,'' both carry the threat of a nuclear strike, and both
		involve the appearance of a cyborg ninja, among numerous other
		similarities. These similarities were so the incident could
		serve as an extreme test case for the Patriots' ability to
		control the flow of information, and consequently bend human
		thoughts and actions as they see fit. They feel that
		information control is necessary to avoid trivial information
		drowning out truth as humanity enters the digital age. Ocelot
		is unaware of this aspect of the plan, believing S3 stands for
		Solid Snake Simulation. This is all explained to Raiden in a 15
		minute radio call, cited by some as one of the most profound
		moments in video game history, and is immediately followed by a
		sword fight with Solidus Snake.
\end{description}
\end{document}
